A Multi-Scale Analysis of 27,000 Urban Street Networks\footnote{This is a journal article manuscript currently under peer review.}

### 2017-03-26 latex/paper.tex
clean up tables

\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage[numbers]{natbib}
\usepackage[affil-it]{authblk}

@@

\begin{table*}[hp]
\caption{Central tendency and statistical dispersion for selected measures of all US urbanized areas' street networks.}
\label{table01}
\csvautotabular{media/table01.csv}
\end{table*}

@@

\begin{figure*}[h]
\includegraphics[width=1\textwidth]{media/fig01.png}
\caption{Intersection density per urbanized area (left) and average streets per node per urbanized area (right) from lowest (pale yellow) to highest (dark red), in the contiguous US}
\label{fig01}
\end{figure*}

@@

\begin{figure*}[hp]
\includegraphics[width=1\textwidth]{media/fig02.png}
\caption{Distribution of node types in 9 urbanized areas, with number of streets emanating from the node on the $x$-axis and proportion of nodes of this type on the $y$-axis }
\label{fig02}
\end{figure*}

@@

\begin{table*}[hp]
\caption{Selected measures of the 30 largest (by land area) urbanized areas' street networks.}
\label{table02}
\csvautotabular{media/table02.csv}
\end{table*}

@@

\begin{table*}[hp]
\caption{Selected summary stats for every incorporated city and town in the US.}
\label{table03}
\csvautotabular{media/table03.csv}
\end{table*}

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig03.png}
	\caption{The linear relationship between total street length and number of nodes in the street networks of 6,857 US neighborhoods (top) and 19,655 US cities and towns (bottom).}
	\label{fig03}
\end{figure*}

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig04.png}
	\caption{Left: contiguous US states by median of mean streets per node in municipal street networks, from lowest (pale yellow) to highest (dark red). Right: contiguous US states by median of mean street segment length in municipal street networks, from longest (pale yellow) to shortest (dark red).}
	\label{fig04}
\end{figure*}

@@

\begin{table*}[hp]
\caption{Median values, aggregated by state plus DC, of selected measures of the municipal-scale street networks for every city and town in the US.}
\label{table04}
\csvautotabular{media/table04.csv}
\end{table*}

@@

\begin{table*}[hp]
\caption{Selected summary stats for all the neighborhood-scale street networks.}
\label{table05}
\csvautotabular{media/table05.csv}
\end{table*}

@@

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig05.png}
	\caption{Square-mile comparisons of central cities and their suburbs. Left: top, downtown Philadelphia; bottom, its suburb, King of Prussia. Middle: top, downtown Portland; bottom, its suburb, Beaverton. Right: top, downtown San Francisco; bottom, its suburb, Concord.}
	\label{fig05}
\end{figure*}

>>>>

\usepackage{graphicx}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage[numbers]{natbib}
\usepackage[affil-it]{authblk}

@@

@@

\begin{figure}
\includegraphics[width=1\textwidth]{media/fig01.png}
\caption{Intersection density per urbanized area (left) and average streets per node per urbanized area (right) from lowest (pale yellow) to highest (dark red), in the contiguous US}
\label{fig01}
\end{figure}

@@

\begin{table}
\centering
\caption{Central tendency and statistical dispersion for selected measures of all US urbanized areas' street networks.}
\label{table01}
\begin{tabular}{llllll}
	\toprule
	measure                                     & mean           & std dev        & min            & median         & max            \\
	\midrule
	Area (km2)                                  & 460.657        & 858.125        & 25.685         & 184.898        & 8937.429       \\
	Avg of the avg neighborhood degree          & 2.886          & 0.109          & 2.626          & 2.875          & 3.228          \\
	Avg of the avg weighted neighborhood degree & 0.032          & 0.018          & 0.021          & 0.03           & 0.321          \\
	Avg circuity                                & 1.076          & 0.019          & 1.023          & 1.074          & 1.14           \\
	Avg clustering coefficient                  & 0.042          & 0.009          & 0.015          & 0.042          & 0.071          \\
	Avg weighted clustering coefficient         & 0.002          & 0.001          & \textless0.001 & 0.001          & 0.006          \\
	Intersection count                          & 12582          & 26054          & 751            & 4593           & 307848         \\
	Avg degree centrality                       & 0.001          & 0.001          & \textless0.001 & 0.001          & 0.007          \\
	Edge density (km/km2)                       & 13.455         & 2.137          & 7.961          & 13.352         & 21.233         \\
	Avg edge length (m)                         & 158.588        & 17.653         & 117.341        & 157.332        & 223.08         \\
	Total edge length (km)                      & 6353           & 12625          & 427            & 2393           & 1.42E+08       \\
	Proportion of dead-ends                     & 0.213          & 0.055          & 0.077          & 0.207          & 0.416          \\
	Proportion of 3-way intersections           & 0.593          & 0.046          & 0.444          & 0.591          & 0.778          \\
	Proportion of 4-way intersections           & 0.187          & 0.063          & 0.054          & 0.178          & 0.422          \\
	Intersection density (per km2)              & 26.469         & 6.256          & 12.469         & 26.029         & 49.423         \\
	Average node degree                         & 5.153          & 0.302          & 4.307          & 5.143          & 6.056          \\
	m                                           & 40890          & 83678          & 2516           & 14955          & 981646         \\
	n                                           & 16032          & 32585          & 874            & 5830           & 373309         \\
	Node density (per km2)                      & 33.628         & 7.641          & 17.675         & 33.071         & 61.655         \\
	Max PageRank value                          & 0.001          & 0.001          & \textless0.001 & 0.001          & 0.003          \\
	Min PageRank value                          & \textless0.001 & \textless0.001 & \textless0.001 & \textless0.001 & \textless0.001 \\
	Self-loop proportion                        & 0.008          & 0.008          & \textless0.001 & 0.006          & 0.071          \\
	Street density (km/km2)                     & 7.262          & 1.221          & 4.217          & 7.171          & 11.797         \\
	Average street segment length (m)           & 161.331        & 17.765         & 119.573        & 160.288        & 225.92         \\
	Total street length (km)                    & 3480           & 7026           & 222            & 1269           & 79046          \\
	Street segment count                        & 22011          & 45725          & 1281           & 7868           & 533757         \\
	Average streets per node                    & 2.764          & 0.162          & 2.223          & 2.77           & 3.217          \\
	\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\includegraphics[width=0.5\textwidth]{media/fig02.png}
\caption{Distribution of node types in 9 urbanized areas, with number of streets emanating from the node on the $x$-axis and proportion of nodes of this type on the $y$-axis }
\label{fig02}
\end{figure}

@@

\newgeometry{margin=1in}
\begin{landscape}
\begin{table}
\centering
\caption{Selected measures of the 30 largest (by land area) urbanized areas' street networks.}
\label{table02}
\begin{tabular}{p{2.5cm} p{1.5cm} p{1.5cm} p{1.5cm} p{1.55cm} p{1.5cm} p{1.5cm} p{1.5cm} p{1.5cm} p{1.5cm} p{1.5cm}}
\hline
urban area core city & land area km2 & avg circuity & avg clustering coefficient & dead-end ratio & 3-way ratio & 4-way ratio & intersect density/ km2 & street density km/km2 & avg street length (m) & avg streets/ node \\
\hline
New York             & 8937          & 1.06         & 0.04                       & 0.18           & 0.62        & 0.2         & 34.44                 & 8.84                  & 148                   & 2.86             \\
Atlanta              & 6850          & 1.1          & 0.04                       & 0.32           & 0.58        & 0.09        & 18.39                 & 6.16                  & 186                   & 2.45             \\
Chicago              & 6325          & 1.07         & 0.04                       & 0.17           & 0.57        & 0.25        & 27.05                 & 7.77                  & 163                   & 2.92             \\
Philadelphia         & 5132          & 1.08         & 0.05                       & 0.17           & 0.63        & 0.2         & 26.65                 & 7.3                   & 159                   & 2.87             \\
Boston               & 4852          & 1.09         & 0.05                       & 0.2            & 0.68        & 0.11        & 24.23                 & 6.44                  & 154                   & 2.71             \\
Dallas               & 4612          & 1.07         & 0.05                       & 0.15           & 0.61        & 0.23        & 34.16                 & 9.16                  & 156                   & 2.95             \\
Los Angeles          & 4497          & 1.06         & 0.03                       & 0.21           & 0.56        & 0.22        & 39.45                 & 10.59                 & 151                   & 2.82             \\
Houston              & 4303          & 1.08         & 0.04                       & 0.2            & 0.57        & 0.22        & 33.49                 & 8.62                  & 145                   & 2.83             \\
Detroit              & 3461          & 1.07         & 0.04                       & 0.15           & 0.63        & 0.22        & 31.1                  & 8.56                  & 159                   & 2.93             \\
Washington           & 3424          & 1.09         & 0.04                       & 0.26           & 0.56        & 0.17        & 31.22                 & 8.26                  & 146                   & 2.66             \\
Miami                & 3204          & 1.1          & 0.05                       & 0.17           & 0.59        & 0.23        & 40.54                 & 10.61                 & 149                   & 2.89             \\
Phoenix              & 2968          & 1.09         & 0.05                       & 0.2            & 0.62        & 0.17        & 35.31                 & 9.1                   & 150                   & 2.77             \\
Minneapolis          & 2647          & 1.08         & 0.05                       & 0.19           & 0.57        & 0.23        & 29.54                 & 8.68                  & 167                   & 2.84             \\
Seattle              & 2617          & 1.07         & 0.03                       & 0.3            & 0.54        & 0.16        & 31.57                 & 8.2                   & 143                   & 2.57             \\
Tampa                & 2479          & 1.1          & 0.05                       & 0.2            & 0.58        & 0.21        & 31.35                 & 8.46                  & 153                   & 2.83             \\
St. Louis            & 2392          & 1.1          & 0.04                       & 0.22           & 0.62        & 0.15        & 29.68                 & 8.16                  & 154                   & 2.73             \\
Pittsburgh           & 2345          & 1.09         & 0.04                       & 0.23           & 0.6         & 0.16        & 23.57                 & 6.71                  & 165                   & 2.72             \\
San Juan             & 2245          & 1.11         & 0.02                       & 0.36           & 0.56        & 0.08        & 26.57                 & 6.43                  & 131                   & 2.36             \\
Cincinnati           & 2040          & 1.07         & 0.03                       & 0.31           & 0.54        & 0.14        & 17.96                 & 6.1                   & 186                   & 2.51             \\
Cleveland            & 2004          & 1.07         & 0.04                       & 0.19           & 0.66        & 0.14        & 19.13                 & 6.51                  & 198                   & 2.76             \\
Charlotte            & 1920          & 1.08         & 0.04                       & 0.3            & 0.57        & 0.11        & 21                    & 6.43                  & 170                   & 2.51             \\
San Diego            & 1897          & 1.08         & 0.03                       & 0.28           & 0.54        & 0.17        & 28.89                 & 8.32                  & 159                   & 2.62             \\
Baltimore            & 1857          & 1.09         & 0.04                       & 0.23           & 0.59        & 0.17        & 27.72                 & 7.56                  & 152                   & 2.72             \\
Indianapolis         & 1828          & 1.08         & 0.05                       & 0.23           & 0.59        & 0.17        & 27.62                 & 7.63                  & 157                   & 2.7              \\
Kansas City          & 1756          & 1.06         & 0.04                       & 0.21           & 0.58        & 0.2         & 32.09                 & 8.57                  & 152                   & 2.79             \\
Denver               & 1729          & 1.07         & 0.05                       & 0.2            & 0.57        & 0.22        & 40.6                  & 9.84                  & 138                   & 2.84             \\
Orlando              & 1548          & 1.11         & 0.06                       & 0.2            & 0.61        & 0.18        & 26.3                  & 7.44                  & 163                   & 2.79             \\
San Antonio          & 1547          & 1.07         & 0.05                       & 0.17           & 0.6         & 0.21        & 28.33                 & 7.91                  & 162                   & 2.87             \\
Nashville            & 1460          & 1.08         & 0.03                       & 0.27           & 0.59        & 0.14        & 19.08                 & 6.1                   & 181                   & 2.6              \\
Milwaukee            & 1413          & 1.06         & 0.06                       & 0.14           & 0.55        & 0.3         & 28.27                 & 7.81                  & 157                   & 3.03 \\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}
\restoregeometry

@@

\begin{table}
\centering
\caption{Selected summary stats for every incorporated city and town in the US.}
\label{table03}
\begin{tabular}{llllll}
	\toprule
	measure                                     & mean    & std dev & min            & median         & max       \\
	\midrule
	Area (km2)                                  & 16.703  & 107.499 & 0.039          & 3.918          & 7434.258  \\
	Avg of the avg neighborhood degree          & 2.94    & 0.297   & 0.4            & 2.953          & 3.735     \\
	Avg of the avg weighted neighborhood degree & 0.033   & 0.141   & \textless0.001 & 0.029          & 9.357     \\
	Avg circuity                                & 1.067   & 0.159   & 1              & 1.055          & 20.452    \\
	Avg clustering coefficient                  & 0.048   & 0.041   & \textless0.001 & 0.04           & 1         \\
	Avg weighted clustering coefficient         & 0.01    & 0.018   & \textless0.001 & 0.005          & 0.524     \\
	Intersection count                          & 324     & 1266    & 0              & 83             & 62996     \\
	Avg degree centrality                       & 0.093   & 0.136   & \textless0.001 & 0.052          & 2.667     \\
	Edge density (km/km2)                       & 12.654  & 6.705   & 0.006          & 11.814         & 58.603    \\
	Avg edge length (m)                         & 161.184 & 80.769  & 25.822         & 144.447        & 3036.957  \\
	Total edge length (km)                      & 159.067 & 578.521 & 0.052          & 40.986         & 24728.326 \\
	Proportion of dead-ends                     & 0.192   & 0.093   & \textless0.001 & 0.184          & 1         \\
	Proportion of 3-way intersections           & 0.572   & 0.11    & \textless0.001 & 0.579          & 1         \\
	Proportion of 4-way intersections           & 0.237   & 0.129   & \textless0.001 & 0.217          & 1         \\
	Intersection density (per km2)              & 29.363  & 21.607  & \textless0.001 & 24.719         & 259.647   \\
	Average node degree                         & 5.251   & 0.668   & 0.8            & 5.268          & 7.166     \\
	m                                           & 1046    & 3924    & 2              & 275            & 176161    \\
	n                                           & 401     & 1516    & 2              & 103            & 71993     \\
	Node density (per km2)                      & 35.449  & 24.409  & 0.047          & 30.718         & 296.74    \\
	Max PageRank value                          & 0.034   & 0.046   & \textless0.001 & 0.021          & 0.87      \\
	Min PageRank value                          & 0.005   & 0.018   & \textless0.001 & 0.002          & 0.5       \\
	Self-loop proportion                        & 0.005   & 0.015   & \textless0.001 & \textless0.001 & 1         \\
	Street density (km/km2)                     & 6.528   & 3.435   & 0.003          & 6.109          & 29.302    \\
	Average street segment length (m)           & 162.408 & 81.035  & 25.822         & 145.479        & 3036.957  \\
	Total street length (km)                    & 86.096  & 331.048 & 0.026          & 21.005         & 15348.008 \\
	Street segment count                        & 558     & 2208    & 1              & 140            & 107393    \\
	Average streets per node                    & 2.851   & 0.282   & 1              & 2.852          & 4         \\
	\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
	\includegraphics[width=0.7\textwidth]{media/fig03.png}
	\caption{The linear relationship between total street length and number of nodes in the street networks of 6,857 US neighborhoods (top) and 19,655 US cities and towns (bottom).}
	\label{fig03}
\end{figure}

\begin{figure}
	\includegraphics[width=0.85\textwidth]{media/fig04.png}
	\caption{Left: contiguous US states by median of mean streets per node in municipal street networks, from lowest (pale yellow) to highest (dark red). Right: contiguous US states by median of mean street segment length in municipal street networks, from longest (pale yellow) to shortest (dark red).}
	\label{fig04}
\end{figure}

\newgeometry{margin=2cm}
\begin{table}
\centering
\caption{Median values, aggregated by state plus DC, of selected measures of the municipal-scale street networks for every city and town in the US.}
\label{table04}
\begin{tabular}{p{1in}p{1in}p{1in}p{1in}p{1in}}
	\toprule
	State & Intersect density (per km2) & Avg streets per node & Avg circuity & Avg street segment length \\
	\midrule
	AK    & 1.28                        & 2.43                 & 1.1          & 223.5                     \\
	AL    & 9.7                         & 2.64                 & 1.07         & 190.81                    \\
	AR    & 15.75                       & 2.78                 & 1.06         & 166.32                    \\
	AZ    & 12.45                       & 2.77                 & 1.08         & 171.8                     \\
	CA    & 32.58                       & 2.74                 & 1.07         & 143.79                    \\
	CO    & 29.26                       & 2.88                 & 1.06         & 136.68                    \\
	CT    & 28.05                       & 2.7                  & 1.07         & 165.87                    \\
	DC    & 58.91                       & 3.26                 & 1.04         & 122.23                    \\
	DE    & 25.3                        & 2.8                  & 1.06         & 127.8                     \\
	FL    & 26.26                       & 2.87                 & 1.07         & 150.75                    \\
	GA    & 15.25                       & 2.78                 & 1.07         & 177.5                     \\
	HI    & 8                           & 2.42                 & 1.07         & 177.93                    \\
	IA    & 24.08                       & 3.02                 & 1.04         & 129.36                    \\
	ID    & 33.85                       & 2.91                 & 1.06         & 132.08                    \\
	IL    & 29.02                       & 2.93                 & 1.05         & 137.77                    \\
	IN    & 35.25                       & 2.93                 & 1.05         & 125.72                    \\
	KS    & 43.94                       & 3.14                 & 1.04         & 124.39                    \\
	KY    & 25.12                       & 2.68                 & 1.07         & 151.28                    \\
	LA    & 17.14                       & 2.79                 & 1.06         & 162.62                    \\
	MA    & 32.33                       & 2.76                 & 1.07         & 135.98                    \\
	MD    & 28.67                       & 2.79                 & 1.07         & 133.69                    \\
	ME    & 7.69                        & 2.67                 & 1.07         & 198.93                    \\
	MI    & 20.93                       & 2.9                  & 1.05         & 153.5                     \\
	MN    & 18.96                       & 2.87                 & 1.06         & 152.92                    \\
	MO    & 29.87                       & 2.89                 & 1.06         & 138.29                    \\
	MS    & 14.76                       & 2.75                 & 1.06         & 174.86                    \\
	MT    & 38.94                       & 3.11                 & 1.04         & 126.89                    \\
	NC    & 19.28                       & 2.65                 & 1.06         & 166.69                    \\
	ND    & 34.28                       & 3.07                 & 1.04         & 123.93                    \\
	NE    & 45.89                       & 3.16                 & 1.04         & 119.79                    \\
	NH    & 12.22                       & 2.69                 & 1.1          & 175.88                    \\
	NJ    & 44.98                       & 2.88                 & 1.04         & 130.79                    \\
	NM    & 18.5                        & 2.93                 & 1.05         & 152.02                    \\
	NV    & 13.86                       & 2.77                 & 1.07         & 147.35                    \\
	NY    & 21.89                       & 2.75                 & 1.06         & 156.88                    \\
	OH    & 25.23                       & 2.8                  & 1.05         & 142.08                    \\
	OK    & 28.22                       & 3.03                 & 1.05         & 139.5                     \\
	OR    & 35.08                       & 2.69                 & 1.06         & 121.18                    \\
	PA    & 35.69                       & 2.87                 & 1.05         & 128.34                    \\
	RI    & 56.23                       & 2.86                 & 1.05         & 110.35                    \\
	SC    & 18.76                       & 2.81                 & 1.06         & 169.21                    \\
	SD    & 32.01                       & 3.12                 & 1.04         & 130.75                    \\
	TN    & 13.62                       & 2.71                 & 1.07         & 192.83                    \\
	TX    & 23.85                       & 2.92                 & 1.05         & 160.44                    \\
	UT    & 12.58                       & 2.71                 & 1.06         & 191.04                    \\
	VA    & 25.18                       & 2.63                 & 1.08         & 145.65                    \\
	VT    & 18.91                       & 2.55                 & 1.08         & 145.18                    \\
	WA    & 28.71                       & 2.75                 & 1.06         & 134.02                    \\
	WI    & 17.87                       & 2.81                 & 1.06         & 156.19                    \\
	WV    & 28.45                       & 2.67                 & 1.08         & 136.57                    \\
	WY    & 23.48                       & 2.92                 & 1.06         & 143.63                    \\
	\bottomrule
\end{tabular}
\end{table}
\restoregeometry

@@

\begin{table}
\centering
\caption{Selected summary stats for all the neighborhood-scale street networks.}
\label{table05}
\begin{tabular}{llllll}
	\toprule
	& mean    & std dev       & min            & median         & max      \\
	\midrule
	Area (km2)                                  & 5.322   & 15.463  & 0.008          & 1.738          & 323.306  \\
	Avg of the avg neighborhood degree          & 2.598   & 0.436   & \textless0.001 & 2.67           & 3.632    \\
	Avg of the avg weighted neighborhood degree & 0.031   & 0.041   & \textless0.001 & 0.029          & 2.991    \\
	Avg circuity                                & 1.08    & 0.411   & 1              & 1.044          & 24.29    \\
	Avg clustering coefficient                  & 0.044   & 0.055   & \textless0.001 & 0.034          & 1        \\
	Avg weighted clustering coefficient         & 0.01    & 0.027   & \textless0.001 & 0.005          & 0.799    \\
	Intersection count                          & 173     & 379     & 0              & 76             & 8371     \\
	Avg degree centrality                       & 0.13    & 0.27    & 0.001          & 0.054          & 4        \\
	Edge density (km/km2)                       & 17.569  & 7.095   & 0.025          & 18.152         & 59.939   \\
	Avg edge length (m)                         & 142.279 & 59.182  & 8.447          & 133.848        & 2231.331 \\
	Total edge length (km)                      & 71.369  & 166.566 & 0.017          & 29.88          & 3563.409 \\
	Proportion of dead-ends                     & 0.17    & 0.131   & \textless0.001 & 0.145          & 1        \\
	Proportion of 3-way intersections           & 0.559   & 0.146   & \textless0.001 & 0.574          & 1        \\
	Proportion of 4-way intersections           & 0.275   & 0.176   & \textless0.001 & 0.234          & 1        \\
	Intersection density (per km2)              & 49.497  & 28.33   & \textless0.001 & 46.43          & 444.355  \\
	Average node degree                         & 4.675   & 0.836   & 0.545          & 4.736          & 7.283    \\
	m                                           & 5201    & 1185    & 1              & 217            & 27289    \\
	n                                           & 208     & 459     & 2              & 90             & 9327     \\
	Node density (per km2)                      & 58.677  & 31.802  & 0.063          & 55.626         & 499.9    \\
	Max PageRank value                          & 0.055   & 0.086   & \textless0.001 & 0.026          & 0.889    \\
	Min PageRank value                          & 0.01    & 0.041   & \textless0.001 & 0.002          & 0.5      \\
	Self-loop proportion                        & 0.007   & 0.034   & \textless0.001 & \textless0.001 & 1        \\
	Street density (km/km2)                     & 9.744   & 4.085   & 0.013          & 9.882          & 33.737   \\
	Average street segment length (m)           & 143.664 & 60.023  & 7.376          & 134.877        & 2231.331 \\
	Total street length (km)                    & 40.049  & 93.987  & 0.009          & 16.248         & 1960.643 \\
	Street segment count                        & 288     & 656     & 1              & 119            & 14754    \\
	Average streets per node                    & 2.925   & 0.408   & 1              & 2.944          & 4.026    \\
	\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
	\includegraphics[width=1\textwidth]{media/fig05.png}
	\caption{Square-mile comparisons of central cities and their suburbs. Left: top, downtown Philadelphia; bottom, its suburb, King of Prussia. Middle: top, downtown Portland; bottom, its suburb, Beaverton. Right: top, downtown San Francisco; bottom, its suburb, Concord.}
	\label{fig05}
\end{figure}
